A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface\tnoteref{t1}

### 2021-11-25 sections/appendix/proportion_within_target_formula/main.tex
Fix some of the `TODOs` (#17)
* Add sections to README.md

* Minor fix in Markov chain formulas

For all formulas consider the arriving state [A_i (u,v)] for individuals
from class i rather than just (u,v). Basically when an individual
arrives at state (u,v) the model will move to a new state based on
that individual's type. This is what this change corresponds to.

* Minor changes on waiting zones

- Display waiting zones 1 and 2 on the queueing system
- Fix some text that listed the incorrect waiting zones

* Changes based on self review

I just read the whole thing and made some minor
chang

Consider the Markov model of figure 
\ref{fig:distribution_of_time_at_specific_state_1_server} with one server and a 
threshold of two individuals. 
Assume that an individual of the first type arrives when the model is at state 
\((0,3)\), thus forcing the model to move to state \((0,4)\). 
The distribution of the time needed for the specified individual to exit the 
system from state \((0,4)\) is given by the sum of exponentially distributed 
random variables with the same parameter \(\mu\). 
The sum of such random variables forms an Erlang distribution which is defined 
by the number of random variables that are added and their exponential 
parameter.
Note here that these random variables represent the individual's pathway from 
the perspective of the individual. 
Thus, \(X_i\) represents the time that it takes to move from the 
\(i^{\text{th}}\) position of the queue to the \((i-1)^{\text{th}}\) position 
(i.e. for someone in front of them to finish their service) and \(X_0\) is the 
time it takes to move from having a service to exiting the system.

@@

Thus, the waiting and service time of an individual in the model of figure 
\ref{fig:distribution_of_time_at_specific_state_1_server} can be captured by an 
erlang distributed random variable. 
The general CDF of the erlang distribution \(Erlang(k, \mu)\) is given by:

@@

Figure \ref{fig:distribution_of_time_at_specific_state_2_servers} represents the 
same Markov model as figure 
\ref{fig:distribution_of_time_at_specific_state_1_server} with the only 
exception that there are 2 servers here. 
By applying the same logic, assuming that an individual arrives at state 
\((0,4)\), the sum of the following random variables arises.

@@

\paragraph{Specific CDF of hypoexponential distribution}
Equations (\ref{eq:general_cdf_hypoexponential}) and 
(\ref{eq:linear_general_cdf_hypoexponential}) refers to the general CDF of the
hypoexponential distribution where the size of the vector parameters can be of
any size \cite{Favaro2010}.
In the Markov chain models described in figures 
\ref{fig:distribution_of_time_at_specific_state_1_server} and 
\ref{fig:distribution_of_time_at_specific_state_2_servers} the parameter vectors 
of the hypoexponential distribution are of size two, and in fact, for any 
possible version of the investigated Markov chain model the vectors can only be 
of size two.
This is true since for any dimensions of this Markov chain model there will 
always be at most two distinct exponential parameters; the parameter for 
finishing a service (\(\mu\)) and the parameter for moving forward in the queue 
(\(C \mu\)). 
For the case of \(C=1\) the hypoexponential distribution will not be 
used as this is equivalent to an erlang distribution.
Therefore, by fixing the sizes of \(\vec{r}\) and \(\vec{\lambda}\) to 2, the 
following specific expression for the CDF of the hypoexponential distribution
arises, where the derivative is removed:

>>>>

Consider the Markov model of Figure 
\ref{fig:distribution_of_time_at_specific_state_1_server} with one server and a 
threshold of two individuals. 
Assume that an individual of the first type arrives when the model is at state 
\((0,3)\), thus forcing the model to move to state \((0,4)\). 
The distribution of the time needed for the specified individual to exit the 
system from state \((0,4)\) is given by the sum of exponentially distributed 
random variables with the same parameter \(\mu\). 
The sum of such random variables forms an Erlang distribution which is defined 
by the number of random variables that are added and their exponential 
parameter.
Note here that these random variables represent the individual's pathway from 
the perspective of the individual. 
Thus, \(X_i\) represents the time that it takes to move from the 
\(i^{\text{th}}\) position of the queue to the \((i-1)^{\text{th}}\) position 
(i.e. for someone in front of them to finish their service) and \(X_0\) is the 
time it takes to move from having a service to exiting the system.

@@

Thus, the waiting and service time of an individual in the model of Figure 
\ref{fig:distribution_of_time_at_specific_state_1_server} can be captured by an 
erlang distributed random variable. 
The general CDF of the erlang distribution \(Erlang(k, \mu)\) is given by:

@@

Figure \ref{fig:distribution_of_time_at_specific_state_2_servers} represents the 
same Markov model as Figure 
\ref{fig:distribution_of_time_at_specific_state_1_server} with the only 
exception that there are 2 servers here. 
By applying the same logic, assuming that an individual arrives at state 
\((0,4)\), the sum of the following random variables arises.

@@

\paragraph{Specific CDF of hypoexponential distribution}
Equations (\ref{eq:general_cdf_hypoexponential}) and 
(\ref{eq:linear_general_cdf_hypoexponential}) refers to the general CDF of the
hypoexponential distribution where the size of the vector parameters can be of
any size \cite{Favaro2010}.
In the Markov chain models described in Figures 
\ref{fig:distribution_of_time_at_specific_state_1_server} and 
\ref{fig:distribution_of_time_at_specific_state_2_servers} the parameter vectors 
of the hypoexponential distribution are of size two, and in fact, for any 
possible version of the investigated Markov chain model the vectors can only be 
of size two.
This is true since for any dimensions of this Markov chain model there will 
always be at most two distinct exponential parameters; the parameter for 
finishing a service (\(\mu\)) and the parameter for moving forward in the queue 
(\(C \mu\)). 
For the case of \(C=1\) the hypoexponential distribution will not be 
used as this is equivalent to an erlang distribution.
Therefore, by fixing the sizes of \(\vec{r}\) and \(\vec{\lambda}\) to 2, the 
following specific expression for the CDF of the hypoexponential distribution
arises, where the derivative is removed:

### 2021-11-25 sections/conclusion/main.tex
Fix some of the `TODOs` (#17)
* Add sections to README.md

* Minor fix in Markov chain formulas

For all formulas consider the arriving state [A_i (u,v)] for individuals
from class i rather than just (u,v). Basically when an individual
arrives at state (u,v) the model will move to a new state based on
that individual's type. This is what this change corresponds to.

* Minor changes on waiting zones

- Display waiting zones 1 and 2 on the queueing system
- Fix some text that listed the incorrect waiting zones

* Changes based on self review

I just read the whole thing and made some minor
chang

The motivation behind this study has been that emergency departments are 
constantly under a lot of pressure to satisfy some regulations. 
This paper shows how this can negatively impact the pathway of both the 
ambulance patients and the ambulance service itself.
Due to some managerial decision making that takes place at the ED, ambulances 
stay blocked outside of the ED at the hospital's parking space in an attempt
to satisfy these regulations.

This study explores a generic 3-player game theoretic model between the 
decision makers of two queueing systems and a service that distributes 
individuals to these two systems (section \ref{sec:model_overview}).
It also describes the construction of the underlying queueing theoretic model 
that has a tandem buffer and a single service centre (section 
\ref{sec:queueing_model}).
Furthermore, the formulas for the performance measures of the queueing model 
are also derived (sections \ref{sec:waiting_time}, \ref{sec:blocking_time}, 
\ref{sec:proportion_within_target}). 
This novel queuing model is the first contribution of the paper.
The game theoretic model is then applied to a healthcare scenario by looking at
the interface between the EDs and the EMS (section 
\ref{sec:ems_ed_application}).
The inefficiencies that emerge from the perspective of the EMS were explored 
along with ways to apply some incentive mechanisms to improve them.
The main takeaways from this paper that were observed when playing the game
between two EDs and the EMS (section \ref{sec:application}) are:
\begin{itemize}
    \item Inefficiencies can be learned and emerge naturally
    \item Targeted incentivisation of behaviours can help escape inefficiencies
\end{itemize}
The former relates to the results of asymmetric replicator dynamics that showed 
that inefficient scenarios can arise by playing the game while the latter 
implies that the learned inefficiencies can be escaped by carefully applying 
certain incentives to the players.
This applied game theoretic model is the second main contribution of this paper.

The model presented here assumes the presence of two players that can receive 
individuals. 
However, in a realistic healthcare scenario an ambulance may have to decide 
among multiple EDs.
An immediate extension of this work would be to consider a multiplayer system
that could represent a group of hospitals in a concentrated area.
Additionally, the game theoretic model that was created uses a discrete 
strategy space for the EDs (something that is also present in various pieces of 
literature~\cite{deo2011centralized, knight2017measuring}).
The single threshold parameter that is used for the ED's decision may not be 
the best way to describe the model.
In reality ED managers could have far more complex parameters for their 
decision making process.
Finally this work assumes that ambulances and EDs act in a selfish and rational
way by only aiming to satisfy their own objectives.
In fact, modelling behaviour in a healthcare setting is a much more complex 
task where some cooperation is often observed.
Another extension would be to explore the behaviour of the ED staff via an 
agent-based model. 
This in turn can be used to model ED staff as agents each with their own 
behavioural traits.

>>>>

The motivation behind this study has been that emergency departments are 
under a lot of pressure to satisfy some regulations. 
This paper shows how this can negatively impact the pathway of both the 
ambulance patients and the ambulance service itself.
Due to some managerial decision making that takes place at the ED, ambulances 
stay blocked outside of the ED at the hospital's parking zone in an attempt
to satisfy these regulations.

This study explores a generic 3-player game theoretic model between the 
decision makers of two queueing systems and a service that distributes 
individuals to these two systems (section \ref{sec:model_overview}).
It also describes the construction of the underlying queueing theoretic model 
that has a tandem buffer and a single service centre (section 
\ref{sec:queueing_model}).
Furthermore, the formulas for the performance measures of the queueing model 
are also derived (sections \ref{sec:waiting_time}, \ref{sec:blocking_time}, 
\ref{sec:proportion_within_target}). 
This novel queuing model is the first contribution of the paper.
The game theoretic model is then applied to a healthcare scenario by looking at
the interface between the EDs and the EMS (section 
\ref{sec:ems_ed_application}).
The inefficiencies that emerge from the perspective of the EMS were explored 
along with ways to apply some incentive mechanisms to improve them.
The key findings from this paper that were observed when playing the game
between two EDs and the EMS (section \ref{sec:application}) are:
\begin{itemize}
    \item Inefficiencies can be learned and emerge naturally
    \item Targeted incentivisation of behaviours can help escape inefficiencies
\end{itemize}
The former relates to the results of asymmetric replicator dynamics that showed 
that inefficient scenarios can arise by playing the game while the latter 
implies that the learned inefficiencies can be escaped by carefully applying 
certain incentives to the players.
This applied game theoretic model is the second main contribution of this paper.

The model presented here assumes the presence of two players that can receive 
individuals. 
However, in a realistic healthcare scenario an ambulance may have to decide 
among multiple EDs.
An immediate extension of this work would be to consider a multiplayer system
that could represent a group of hospitals in a concentrated area.
Additionally, the game theoretic model that was created uses a discrete 
strategy space for the EDs (something that is also present in various related 
literature~\cite{deo2011centralized, knight2017measuring}).
The single threshold parameter that is used for the ED's decision may not be 
the best way to describe the model.
In reality ED managers could have far more complex parameters for their 
decision making process.
Finally this work assumes that the EMS and EDs act in a selfish and rational
way by only aiming to satisfy their own objectives.
In fact, modelling behaviour in a healthcare setting is a much more complex 
task where some cooperation may often be observed.
Another extension would be to explore the behaviour of the ED staff via an 
agent-based model. 
This in turn can be used to model ED staff as agents each with their own 
behavioural traits.

### 2021-11-25 sections/methodology/main.tex
Fix some of the `TODOs` (#17)
* Add sections to README.md

* Minor fix in Markov chain formulas

For all formulas consider the arriving state [A_i (u,v)] for individuals
from class i rather than just (u,v). Basically when an individual
arrives at state (u,v) the model will move to a new state based on
that individual's type. This is what this change corresponds to.

* Minor changes on waiting zones

- Display waiting zones 1 and 2 on the queueing system
- Fix some text that listed the incorrect waiting zones

* Changes based on self review

I just read the whole thing and made some minor
chang

Th problem defined in section \ref{sec:model_overview} describes a normal-form
game between the decision makers of two queueing systems and a third player that 
decides how to distribute individuals to the systems.
The strategy space of the two queueing systems is defined as the possible values
that the threshold parameter can take \(T_i \in [1, N_i]\).
Then, the distributor has to decide on the proportion of individuals to send to 
each queueing system \(p_A \text{ and } p_B\), where \(p_A, p_B \in [0, 1] \)
and \(p_A + p_B = 1\).
Figure \ref{fig:imperfect_info_game} form section \ref{sec:model_overview} 
shows a diagrammatic representation of the game to be played and the decisions 
to be made.
As described in section \ref{sec:model_overview} queueing system \(A\) decides
on a strategy, at the same time, queueing system \(B\) chooses its own 
threshold, unaware of the first queueing system's choice.
Finally, the distributor makes its choice based on the strategies that the 
queueing systems chose to play.

The utilities to each player can be represented by 3 matrices; the two payoff 
matrices of the normal form game and the routing matrix.
The payoff matrices and their utilities are defined by equations 
(\ref{eq:payoff_entry}) and (\ref{eq:payoff_matrices}) in section 
\ref{sec:model_overview}.

The routing matrix holds the values \((p_A, p_B)\) which are the proportion 
of class 2 individuals to send to queueing system \(A\) and \(B\).
Each pair \((p_A, p_B)\) can be calculated using equation 
(\ref{eq:obj_distributor}) and is essentially
a best response to the actions of the queueing systems.
Equation \ref{eq:obj_distributor} is defined and explained in section 
\ref{sec:model_overview}.
Thus, using equation \ref{eq:obj_distributor} for all possible sets of 
thresholds we can get the full routing matrix that consists of the proportions
to send to queueing system A (\(p_A\)) and to queueing system B (\(p_B\)).

@@

In order to populate the payoff matrices and the routing matrix the method
of backwards induction is used.
Consider figure \ref{fig:imperfect_info_game} and the flow of the game that was
described (i.e. \(Q_A, Q_B \rightarrow D\)).
Due to the fact that the payoff matrices \(A\) and \(B\) depend on the routing 
matrix \(R\) the entries of the matrices are calculated in a backwards way 
(\(D \rightarrow Q_A, Q_B\)). 
Thus for every pair of strategies \(T_A, T_B\), the proportion of individuals 
that are to be transported to each queueing system is calculated first.

@@

Another approach to measuring emergent behaviour is to consider 
the emergence itself and not only stable end points. 
Indeed, some Nash equilibria might not arise naturally. 
Thus, in order to analyse the strategies played by the two EDs, the learning 
algorithm: asymmetric replicator dynamics is 
used~\cite{asymmetricreplicatordynamics}.
The two players are modelled as two separate populations where each 
individual in the population is assigned a strategy.
As the game progresses the proportion of each player playing each strategy 
changes based on their previous interactions.
The fitness of each strategy is defined as:

>>>>

The problem defined in section \ref{sec:model_overview} describes a normal-form
game between the decision makers of two queueing systems and a third player that 
decides how to distribute individuals to the systems.
The strategy space of the two queueing systems is defined as the possible values
that the threshold parameter can take \(T_i \in [1, N_i]\).
Then, the distributor has to decide on the proportion of individuals to send to 
each queueing system \(p_A \text{ and } p_B\), where \(p_A, p_B \in [0, 1] \)
and \(p_A + p_B = 1\).
Figure \ref{fig:imperfect_info_game} 
shows a diagrammatic representation of the game to be played and the decisions 
to be made.
As described in Section \ref{sec:model_overview}, queueing system \(A\) decides
on a strategy and at the same time, queueing system \(B\) chooses its own 
threshold but unaware of the first queueing system's choice.
Finally, the distributor makes its choice based on the strategies that the 
queueing systems chose to play.

The utilities to each player can be represented by 3 matrices; the two payoff 
matrices of the normal form game and the routing matrix.
The payoff matrices and their utilities are defined by equations 
(\ref{eq:payoff_entry}) and (\ref{eq:payoff_matrices}).

The routing matrix holds the values \((p_A, p_B)\) which are the proportion 
of class 2 individuals to send to queueing system \(A\) and \(B\).
Each pair \((p_A, p_B)\) can be calculated using equation 
(\ref{eq:obj_distributor}) and is essentially
a best response to the actions of the queueing systems.
Thus, using equation \ref{eq:obj_distributor} for all possible sets of 
thresholds we can get the full routing matrix that consists of the proportions
to send to queueing system A (\(p_A\)) and to queueing system B (\(p_B\)).

@@

In order to populate the payoff matrices and the routing matrix the method
of backwards induction is used.
Consider Figure \ref{fig:imperfect_info_game} and the flow of the game that was
described (i.e. \(Q_A, Q_B \rightarrow D\)).
Due to the fact that the payoff matrices \(A\) and \(B\) depend on the routing 
matrix \(R\) the entries of the matrices are calculated in a backwards way 
(\(D \rightarrow Q_A, Q_B\)). 
Thus for every pair of strategies \(T_A, T_B\), the proportion of individuals 
that are to be transported to each queueing system is calculated first.

@@

Another approach to measuring emergent behaviour is to consider 
the emergence itself and not only stable end points. 
Indeed, some Nash equilibria might not arise naturally. 
Thus in order to analyse the strategies played by the two EDs, the learning 
algorithm asymmetric replicator dynamics is 
used~\cite{asymmetricreplicatordynamics}.
The two players are modelled as two separate populations where each 
individual in the population is assigned a strategy.
As the game progresses the proportion of each player playing each strategy 
changes based on their previous interactions.
The fitness of each strategy is defined as:

### 2021-11-25 sections/model_overview/main.tex
Fix some of the `TODOs` (#17)
* Add sections to README.md

* Minor fix in Markov chain formulas

For all formulas consider the arriving state [A_i (u,v)] for individuals
from class i rather than just (u,v). Basically when an individual
arrives at state (u,v) the model will move to a new state based on
that individual's type. This is what this change corresponds to.

* Minor changes on waiting zones

- Display waiting zones 1 and 2 on the queueing system
- Fix some text that listed the incorrect waiting zones

* Changes based on self review

I just read the whole thing and made some minor
chang

This is a standard normal form game~\cite{Maschler2013},  
in that each player in this game has their own objectives which they aim to 
optimise.
More specifically, the queueing systems' objective is captured by an upper bound
of the time that a fixed proportion of individuals spend in the system, 
while the distributor aims to minimise the time that its individuals 
are blocked.
% TODO: Depending on how this is described earlier, we might need a little more 
% here (as to what we mean by "blocked")

@@

Both queueing systems follow a queueing model that has two waiting spaces for 
individuals. 
The first waiting zone is where the individuals queue right before receiving 
their service and has a capacity of \( N - C \), where \(N\) is the total 
capacity of the waiting space and \(C\) is the number of servers. 
The second waiting zone is where the individuals, that are sent from the 
distributor, stay until they are allowed to enter the first waiting zone.
The second waiting zone has a capacity of \(M\) and no servers.

@@

        % First line (horizontal) from lambda_1
        \draw (4.2, 1.8) -- +(-169.5pt,0) node[left] {\( \lambda_1 \)};
        % Second line (vertical) from lambda_1
        \draw (4.2, 1.8) -- (4.2, 0.525);
        % Arrow line to Queue 2
        \draw[->] (4.2, 0.525) -- (4.8, 0.525);  
    \end{tikzpicture}
    \caption{A diagrammatic representation of the queueing model. 
    The threshold \(T\) only applies to arrivals from the first buffer. 
    If the second buffer is at that threshold only individuals of the first type 
    are accepted (at a rate \(\lambda_1\)) and individuals of the second type 
    (arriving at a rate \(\lambda_2\)) are held blocked in the first buffer.}
    \label{fig:diagram_of_queueing_system}
\end{figure}

Note here that both types of individuals can become lost to the system. 
Individual allocated from the distributor become lost to the system whenever 
an arrival occurs and the second waiting zone is at full capacity (\(M\) 
individuals already waiting).
Similarly, other individuals get lost whenever they arrive at the first waiting 
zone and it is at full capacity (\(N - C\) individuals already waiting).

@@

The third player, the distributor, has their own choices to make and their own 
goals to satisfy.
The strategy set of the third player is the proportion \(0 \leq p_A \leq 1\) of 
individuals it sends to the first queueing system (the proportion 
\(p_B = 1 - p_A\) is sent to the second queueing system).
In addition, the distributor aims to minimise any potential blockages
that may occur, given the pair of thresholds chosen by the two queueing systems.
Thus, its objective is to minimise the blocked time of the individuals (\(B_i\))
that they send to the two queueing systems.
Apart from the time being blocked, an additional aspect that may affect the 
decision of the distributor is the proportion of lost individuals (\(L_i\)).
Equation \ref{eq:obj_distributor} can be used to capture a mixture 
between the two objectives \(L_i\) and \(B_i\) where \(i \in \{A, B\}\).
\begin{equation*}\label{eq:obj_distributor}
    (p_A, p_B) \quad s.t. \quad 
    \alpha L_A(p_A) + (1 - \alpha) B_A(p_A) = 
    \alpha L_B(p_B) + (1 - \alpha) B_B(p_B)
\end{equation*}

@@

Using either equation (\ref{eq:obj_queueing_systems}) or equation
(\ref{eq:obj_distributor}) gives an imperfect information extensive form game. 
An imperfect information game is defined as an extensive form game where some 
of the information about the game state is hidden for at least one of the 
players~\cite{Berwanger2008}. In this study the state of the problem that is
hidden is the threshold that each of the first two players chooses to play.
In other words, each queueing system chooses to play a strategy without 
knowing the other system's strategy.
The distributor then, fully aware of the chosen threshold strategies, 
distributes individuals among the two systems in order to minimise the time 
that its individuals will be blocked. Figure \ref{fig:imperfect_info_game} 
illustrates this.

@@

Based on the choice of strategy of these two players the distributor will then 
make their own choice of the proportion of individuals to send to each system.

>>>>

This is a standard normal form game~\cite{Maschler2013},  
in that each player in this game has their own objectives which they aim to 
optimise.
More specifically, the queueing systems' objective is captured by an upper bound
of the time that a fixed proportion of individuals spend in the system, 
while the distributor aims to minimise the time that its individuals 
are blocked.
Although we generalise for any such system, relating this back to the
motivating case study, here the decision makers of the queueing systems
represent the ED managers and the distributor is the EMS who allocate (send)
ambulances to one of the EDs (see Section \ref{sec:ems_ed_application}). 
% TODO: Depending on how this is described earlier, we might need a little more 
% here (as to what we mean by "blocked")

@@

Both queueing systems follow a queueing model that has two waiting zones for 
individuals. 
The first waiting zone is where the individuals queue right before receiving 
their service and has a capacity of \( N - C \), where \(N\) is the total 
capacity of the waiting space and \(C\) is the number of servers. 
The second waiting zone is where the individuals, that are sent from the 
distributor, stay until they are allowed to enter the first waiting zone.
The second waiting zone has a capacity of \(M\) and no servers.

@@

        % First line (horizontal) from lambda_1
        \draw (4.2, 1.8) -- +(-169.5pt,0) node[left] {\( \lambda_1 \)};
        % Second line (vertical) from lambda_1
        \draw (4.2, 1.8) -- (4.2, 0.525);
        % Arrow line to Queue 2
        \draw[->] (4.2, 0.525) -- (4.8, 0.525);  
    \end{tikzpicture}
    \caption{A diagrammatic representation of the queueing model. 
    The threshold \(T\) only applies to arrivals from the first buffer. 
    If the second buffer is at that threshold, only individuals of the first type 
    are accepted (at a rate \(\lambda_1\)) and individuals of the second type 
    (arriving at a rate \(\lambda_2\)) are blocked in the first buffer.}
    \label{fig:diagram_of_queueing_system}
\end{figure}

Note here that both types of individuals can become lost to the system. 
An individual allocated from the distributor becomes lost to the system whenever 
an arrival occurs and the second waiting zone is at full capacity (\(M\) 
individuals already waiting).
Similarly, individuals get lost whenever they arrive at the first waiting 
zone and it is at full capacity (\(N - C\) individuals already waiting).

@@

The third player, the distributor, has their own choices to make and their own 
goals to satisfy.
The strategy set of the third player is the proportion \(0 \leq p_A \leq 1\) of 
individuals it sends to the first queueing system (the proportion 
\(p_B = 1 - p_A\) is sent to the second queueing system).
In addition, the distributor aims to minimise any potential blockages
that may occur, given the pair of thresholds chosen by the two queueing systems.
Thus, its objective is to minimise the blocked time of the individuals (\(B_i\))
that they send to the two queueing systems.
Apart from the time being blocked, an additional aspect that may affect the 
decision of the distributor is the proportion of lost individuals (\(L_i\)).
Equation \ref{eq:obj_distributor} can be used to capture a mixture 
between the two objectives \(L_i\) and \(B_i\) where \(i \in \{A, B\}\):
\begin{equation*}\label{eq:obj_distributor}
    (p_A, p_B) \quad s.t. \quad 
    \alpha L_A(p_A) + (1 - \alpha) B_A(p_A) = 
    \alpha L_B(p_B) + (1 - \alpha) B_B(p_B)
\end{equation*}

@@

Using either equation (\ref{eq:obj_distributor}) or 
(\ref{eq:obj_queueing_systems}) gives an imperfect information extensive form 
game. 
An imperfect information game is defined as an extensive form game where some 
of the information about the game state is hidden for at least one of the 
players~\cite{Berwanger2008}. In this study the state of the problem that is
hidden is the threshold that each of the first two players chooses to play.
In other words, each queueing system chooses to play a strategy without 
knowing the other system's strategy.
The distributor then, fully aware of the chosen threshold strategies, 
distributes individuals among the two systems in order to minimise the time 
that its individuals will be blocked. Figure \ref{fig:imperfect_info_game} 
illustrates this.

@@

Based on the choice of strategy of these two players, the distributor will then 
make their own choice of the proportion of individuals to send to each system.

### 2021-11-25 sections/queueing_model/blocking_time/main.tex
Changes based on self review
I just read the whole thing and made some minor
changes here and there.
Fix some of the `TODOs` (#17)
* Add sections to README.md

* Minor fix in Markov chain formulas

For all formulas consider the arriving state [A_i (u,v)] for individuals
from class i rather than just (u,v). Basically when an individual
arrives at state (u,v) the model will move to a new state based on
that individual's type. This is what this change corresponds to.

* Minor changes on waiting zones

- Display waiting zones 1 and 2 on the queueing system
- Fix some text that listed the incorrect

The term \(b(u,v)\) is the mean time that an individual will be blocked when 
the system is at state \((u,v)\). 
For all the states of the system \(b(u,v)\) is given by:

@@

Figure \ref{fig:markov_vs_des_blocking_time_comparison} illustrates a comparison 
between the formulas that arise from the Markov chain model and the equivalent 
values of the blocking time extracted from discrete event simulation
(appendix~\ref{sec:appendix_des}).
The blocking time is calculated using both methods for a range of values of
\(\lambda_2\).
The simulation was ran 100 times and the recorded mean blocking time at each 
iteration is used to populate the violin plots.

>>>>

The term \(b(u,v)\) is the mean time that an individual will be blocked for, 
when the individual arrives in the system at state \((u,v)\). 
For all the states of the system \(b(u,v)\) is given by:

@@

Figure \ref{fig:markov_vs_des_blocking_time_comparison} illustrates a comparison 
between the formulas that arise from the Markov chain model and the equivalent 
values of the blocking time extracted from discrete event simulation
(appendix~\ref{sec:appendix_des}).
The blocking time is calculated using both methods for a range of values of
\(\lambda_2\).
The simulation was ran 100 times and the recorded mean blocking time at each 
iteration is used to populate the violin plots.
It can be seen that the blocking times generated by the simulation match the
ones generated by the Markov chains model.
